Red-Giant Hot Jupiters: Brilliant Radio Beacons?

### 2015-05-24 ms.tex
figures of radio emission from actual M-type RGs are added

For each red giant, the mass-loss rate is estimated by Reimers' equation \citep{reimers1975}:
%%%
\begin{equation}
\dot M_{\star } \sim \left( \frac{R_{\star }}{R_{\odot }} \right)\left( \frac{L_{\star }}{L_{\odot }} \right) \left( \frac{M_{\star }}{M_{\odot }} \right)^{-1}
\end{equation}
%%%
where $R_{\star }$, $L_{\star } (=4\pi R_{\star }^2 T_{\star }^4)$, and $M_{\star}$ are radius, luminosity, and mass of the star. 
The velocity of stellar wind is assumed to scale with the escape velocity, hence
%%%
\begin{equation}
v \propto \sqrt{\frac{2GM_{\star }}{R_{\star }}}
\end{equation}
%%%
Using these values for equations (\ref{eq:stand-off}) and (\ref{eq:stand-off-radius}) as well as the distance to the target, we can estimate the frequency and intensity by specifying the magnetic field and orbital distance of a hypothetical planetary companion. 
Here, we consider two cases: (a) a Jupiter-twin at 5.2~AU whose cyclotron frequency is $\sim 30$~MHz, and (b) a larger Jovian planet with $M_p\sim 5M_p$ of 4.5 Gyrs old at 5.2~AU whose cyclotron frequency is $\sim 300$~MHz (equation (\ref{eq:scalingfc})).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htbp]
   \plotoneh{model_planetaryB.pdf}
   \caption{.}
  \label{fig:observability}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

For each red giant, the mass-loss rate is estimated by Reimers' equation \citep{reimers1975}:
%%%
\begin{equation}
\dot M_{\star } [M_{\odot }{\rm /yr}] \sim 4 \times 10^{-13} \left( \frac{R_{\star }}{R_{\odot }} \right)\left( \frac{L_{\star }}{L_{\odot }} \right) \left( \frac{M_{\star }}{M_{\odot }} \right)^{-1}
\end{equation}
%%%
where $R_{\star }$, $L_{\star } (=4\pi R_{\star }^2 T_{\star }^4)$, and $M_{\star}$ are radius, luminosity, and mass of the star. 
The velocity of stellar wind is assumed to scale with the escape velocity, hence
%%%
\begin{equation}
v \propto \sqrt{\frac{2GM_{\star }}{R_{\star }}}
\end{equation}
%%%
Using these values for equations (\ref{eq:stand-off}) and (\ref{eq:stand-off-radius}) as well as the distance to the target, we can estimate the frequency and intensity by specifying the magnetic field and orbital distance of a hypothetical planetary companion. 
Here, we consider two cases: (a) a Jupiter-twin at 5~AU whose cyclotron frequency is $\sim 30$~MHz, and (b) a larger Jovian planet with $M_p\sim 5M_p$ of 4.5 Gyrs old at 5~AU whose cyclotron frequency is $\sim 300$~MHz (equation (\ref{eq:scalingfc})).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htbp]
   \plotoneh{model_planetaryB.pdf}
   \plotoneh{model_planetaryB.pdf}
   \caption{.}
  \label{fig:observability}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
